Automated Formal Synthesis\\ of Safe Digital Controllers for Continuous Plants

### 2019-01-23 automatica/paper.tex
misaligned notation

We provide the results in Table~\ref{tab:results}, where: 
\textit{Benchmark} is the name of the corresponding benchmark; 
\textit{Order} is the number of continuous variables of the model; 
\textcolor{blue}{$\mathcal{F}_{\langle I_p,F_p \rangle}$, where $I_p$ and $F_p$ indicate the integer and fractional parts,  
and \textcolor{blue}{ $\mathcal{F}_{\langle W_p,F_p \rangle}$}, where $W_p$ and $F_p$ indicate the total word-length and fractional part, 
are the fixed- and floating-point precisions used to model the plant, respectively; } 
and \textit{Time} is the total time required to synthesize a controller for the given plant.    
Timeouts are indicated by~\xmark, while failures to synthesise the digital controllers are indicated by $\dagger$ \note{no such instances}.  
The precision for the controller, $\mathcal{F}_{\langle I_c,F_c \rangle}$, is
chosen to be $I_c = 8$, $F_c = 8$ for fixed-point, \textcolor{blue}{whereas  
$\mathcal{F}_{\langle W_c, F_c \rangle}$ is chosen to be $W_c = 16$ and $F_c = 10$
for half-precision floating-point format}.

>>>>

We provide the results in Table~\ref{tab:results}, where: 
\textit{Benchmark} is the name of the corresponding benchmark; 
\textit{Order} is the number of continuous variables of the model; 
\textcolor{blue}{$\mathcal{F}_{\langle I_p,F_p \rangle}$, where $I_p$ and $F_p$ indicate the integer and fractional parts,  
and \note[make this align with the notation earlier in the paper]}\textcolor{blue}{ $\mathcal{F}_{\langle W_p,F_p \rangle}$}, where $W_p$ and $F_p$ indicate the total word-length and fractional part, 
are the fixed- and floating-point precisions used to model the plant, respectively; } 
and \textit{Time} is the total time required to synthesize a controller for the given plant.    
Timeouts are indicated by~\xmark, while failures to synthesise the digital controllers are indicated by $\dagger$ \note{no such instances}.  
The precision for the controller, $\mathcal{F}_{\langle I_c,F_c \rangle}$, is
chosen to be $I_c = 8$, $F_c = 8$ for fixed-point, \textcolor{blue}{whereas  
$\mathcal{F}_{\langle W_c, F_c \rangle}$ is chosen to be $W_c = 16$ and $F_c = 10$
for half-precision floating-point format}.
